% Copyright (C) 2022 CDN (Diego) Damasceno

\documentclass[11pt,a4paper]{article}

\usepackage[english]{babel}
\usepackage{inputenc}
\usepackage[T1]{fontenc}
\usepackage{currvita}
\usepackage[square,sort,comma,numbers]{natbib}
\bibliographystyle{acm}
\usepackage{bibentry}
\usepackage{xcolor}
\usepackage[colorlinks = true,
linkcolor = blue,
urlcolor  = blue,
citecolor = blue,
anchorcolor = blue]{hyperref}
\usepackage{enumitem}
\nobibliography*

% \usepackage[margin=2.0cm]{geometry}
\usepackage[left=2cm,right=2cm]{geometry}
% \usepackage[bottom=2.5cm,top=2.5cm]{geometry}

\usepackage{titlesec}

% Conditional printing 
\newif\ifREFs% \REFsfalse (List of References)
\newif\ifPersonalInfo % \PersonalInfofalse (Personal information)

\PersonalInfotrue % Prints phone, gmail/skype, custom closing message
\REFstrue % Prints references

% Sections formatting
\titleformat{\section}{\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule]
\titleformat{\subsection}{\bfseries\raggedright\large}{}{0em}{}[]

% Phone and Email as hyperlinks
\usepackage{color}
\newcommand\phone[1]{\href{tel:#1}{{\emailfont #1}}}
\newcommand\email[1]{\href{mailto:#1}{{\emailfont #1}}}
\newcommand\emailfont{\sffamily}

% CV Info (to be customized).
\newcommand{\CVAuthor}{\textbf{Rapha\"{e}l Scherrer, MSc}}

\begin{document}
	\begin{cv}{Curriculum Vitae}
		
		\section{Personal Information}
		
		\begin{cvlist}{}
			
			\item \CVAuthor\\
			PhD candidate in Theoretical Evolutionary Biology at the University of Groningen
			
            Address: Turfsingel 1020, 9711VZ, Groningen, the Netherlands
			
			\item 
			Tel.:~\phone{+31 (6) 36 23 42 23}\\
			Email:~\email{raphael.scherrer@evobio.eu}\\
			GitHub: \url{https://github.com/rscherrer}\\
			ORCiD: \url{https://orcid.org/0000-0002-1447-7630}\\
			ResearchGate: \url{https://researchgate.net/profile/Raphael-Scherrer}\\
			Linkedin: \url{https://www.linkedin.com/in/rapha%C3%ABl-scherrer-5817a3bb/}
			
			\item 
			Born: 12 May 1994 in Toul, France\\
			Nationality: French
			
		\end{cvlist}

        \section{Professional Experience}

        \begin{cvlist}{}

            \item[08/2023--08/2024]
            \textbf{Scientific Programmer}\\
            Groningen Institute for Evolutionary Life Sciences\\
            University of Groningen, the Netherlands

            \item[03/2023--08/2023]
            \textbf{University Lecturer}\\
            University of Groningen, the Netherlands
            
            \item[11/2017--02/2022]
            \textbf{PhD Scholarship Student}\\
            Adaptive Life Program\\
            University of Groningen, the Netherlands

        \end{cvlist}
		
		% \vspace{-0.75cm}
		\section{Education}
		
		\begin{cvlist}{}
			
			\item[11/2017--now] 
			\textbf{PhD in Theoretical Evolutionary Biology}\\
            Title: 
			\textit{The genomic architecture of adaptive speciation}.\\
			Department of Theoretical Research in Evolutionary Life Sciences\\
			Groningen Institute for Evolutionary Life Sciences\\
			University of Groningen, the Netherlands\\
			Supervised by Prof. Rampal S. Etienne \& Prof. G. Sander van Doorn
			
			\item[09/2015--08/2017] 
			\textbf{MSc in Evolutionary Biology}\\
			MEME Erasmus Mundus Master's in Evolutionary Biology (\url{https://evobio.eu})\\
			University of Groningen, the Netherlands (GPA 4/4)\\
			Ludwig Maximilian University, Munich, Germany (3.9/4)\\
			Harvard University, Cambridge, MA, USA (thesis)\\
			Uppsala University, Sweden (thesis)
			
			\item[09/2014--08/2015] 
			\textbf{MSc in Ecology and Evolution} (First year)\\
			University of Montpellier, France (GPA 3.83/4)
			
			\item[09/2011--08/2014] 
			\textbf{BSc in Biology}\\
			University of Lorraine, Nancy, France (GPA 3.92/4)\\
			Graduated \textit{summa cum laude} (Mention Tr\`{e}s Bien)
			 
			\item[07/2011] 
			\textbf{Scientific Baccalaur\'{e}at}\\
			Lyc\'{e}e Louis Majorelle, Toul, France\\
			Graduated \textit{summa cum laude} (Mention Tr\`{e}s Bien)
			
		\end{cvlist}
	
		\section{Peer Reviewed Publications}
		
		\begin{cvlist}{}
			
			\item \textbf{Scherrer, R.}, Donihue, C. M., Reynolds, R. G., Losos, J. B., \& Geneva, A. J. (2022). Dewlap colour variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies. \textit{Journal of Evolutionary Biology}, 35(5), 680–692.\\ \url{https://doi.org/10.1111/jeb.14002}
			
			\item Simonet, C., \textbf{Scherrer, R.}, Rego-Costa, A., \& Etienne, R. S. (2018). Robustness of the approximate likelihood of the protracted speciation model. \textit{Journal of Evolutionary Biology}, 31(3), 469–479.\\ \url{https://doi.org/10.1111/jeb.13233}
			
			\item \textbf{Scherrer, R.}, Hurtado, A., Garcia Machado, E., \& Debiais-Thibaud, M. (2017). MicroCT survey of larval skeletal mineralization in the Cuban gar \textit{Atractosteus tristoechus} (Actinopterygii; Lepisosteiformes). \textit{MorphoMuseuM}, 3(3), e3.\\ \url{https://doi.org/10.18563/m3.3.3.e3}
			
		\end{cvlist}

        \section{In Prep (Lead Author)}

        \begin{cvlist}{}

            \item[]
            \textbf{Scherrer, R.}, Dieckmann, U., Etienne, R. S. \& van Doorn, G. S. Epistasis and the genomic architecture of adaptive speciation with gene flow. In \textit{The genomic architecture of adaptive speciation} (Doctoral dissertation in prep.). University of Groningen, the Netherlands.

            \item[]
            \textbf{Scherrer, R.}, Korte, M., Smit, C., van Doorn, G. S. \& Etienne, R. S. Ecological facilitation hinders adpatation to climate change in a semi-arid environment.  In \textit{The genomic architecture of adaptive speciation} (Doctoral dissertation in prep.). University of Groningen, the Netherlands.

            \item[]
            \textbf{Scherrer, R.}, Damhuis, J., van Doorn, G. S. \& Etienne, R. S. Diversification of ecological specialists under optimal resource choice. In \textit{The genomic architecture of adaptive speciation} (Doctoral dissertation in prep.). University of Groningen, the Netherlands.

            \item[]
            \textbf{Scherrer, R.}, Janzen, T. \& Etienne, R. S. Protracted speciation explains phylogenetic imbalance and slowdowns in lineage accumulation, but not both at the same time. In \textit{The genomic architecture of adaptive speciation} (Doctoral dissertation in prep.). University of Groningen, the Netherlands.

            \item[]
            \textbf{Scherrer, R.}, Delhey, K., Johansson, U., Etienne, R. S. \& Monroe, M. J. Rapid divergence of plumage coloration upon speciation in birds-of-paradise. In \textit{The genomic architecture of adaptive speciation} (Doctoral dissertation in prep.). University of Groningen, the Netherlands.
 
        \end{cvlist}

        \section{In Prep (Co-Author)}

        \begin{cvlist}{}

            \item[]
            Bravo, H., \textbf{Scherrer, R.}, Xu, T., Scholten, Y., Santos Neves, P., Gu\'{e}rin, C., Borgstein, N. \& van der Meij, S. E. T. (2024). Evaluating robustness of a Caribbean coral-symbiont fauna network in a changing climate. In \textit{On the symbiosis of species in coral reefs} (Doctoral dissertation). University of Groningen, the Netherlands.\\
            \url{https://doi.org/10.33612/diss.993901641}

            \item[]
            Ruiz Puerta, E. J., \textbf{Scherrer, R.}, Cabrera, A. A., McCarthy, M. L., En Pan, S., Howse, L. R., Szpak, P., Keighley, X., Pálsson, S., Rufolo, S., Malmquist, H. J., Gotfredsen, A. B., Cory, M. J. D., Desjardins, S. P. A., Jordan, P. D. \& Tange Olsen, M. (2024). Ancient DNA reveals 5000 years of male-biased walrus hunting across the Atlantic Arctic. In 
            \textit{The use of ancient genomes to unveil the evolutionary history and social implications of Atlantic walruses hunting during the last 5000 years in the Arctic} (Doctoral dissertation). University of Groningen, the Netherlands.\\
            \url{https://doi.org/10.33612/diss.1073769863}

            \item[]
            Riederer, J. M., \textbf{Scherrer, R.}, van der Vaart, C., Favot, R., Kreider, J., Mahler, L., Kolbe, J., Komdeur, J. \& Weissing, F. J. Sexual selection and evolvability in \textit{Anolis} lizards. In \textit{Evolvability and sexual selection: how social interactions shape the ability to evolve} (Doctoral dissertation in prep.). University of Groningen, the Netherlands.

            \item
            van der Meij, S., Bravo, H., Borgstein, N., Scholten, Y., \textbf{Scherrer R.}, \& Xu T. Caribbean coral-dwelling fauna: literature overview and new records (Manuscript in prep.).
            
        \end{cvlist}

        \section{Software Contributions}

        \begin{cvlist}{}

            \item 
            Etienne, R. S., Valente, L., Phillimore, A. B., Haegeman, B., Lambert, J. W., Santos Neves, P., Xie S., Bilderbeek, R. J. C., Hildenbrandt, H., Hauffe, T., Laudanno, G., Kristensen, N. \& \textbf{Scherrer, R} (2025). DAISIE: Dynamic Assembly of Island biota through Speciation, Immigration and Extinction. \textit{The Comprehensive R Archive Network} (CRAN).\\
            \url{https://doi.org/10.32614/CRAN.package.DAISIE}
            
        \end{cvlist}
        
		\section{Other Research}
		
		\begin{cvlist}{}
			
			\item[03/2017--08-2017] 
			\textbf{MSc thesis:} Sexual selection and the rapid evolution of plumage coloration upon speciation: a study of birds of paradise (Paradisaeidae).\\ Department of Evolutionary Biology, Uppsala University, Uppsala, Sweden. Supervised by Dr. Melanie J. Monroe.
			
			\item[09/2016--02/2017] 
			\textbf{MSc thesis:} Adaptive divergence of a sexual trait in a Caribbean lizard.\\
			Department of Organismic and Evolutionary Biology, Harvard University, Cambridge, MA, USA.	Supervised by Dr. Anthony J. Geneva, Dr. Colin M. Donihue \& Prof. Jonathan B. Losos.
			
			\item[03/2016--08/2016] 
			\textbf{MSc project:} Gene expression divergence between populations and sexes in \textit{Drosophila melanogaster}.\\
			Department of Evolutionary Biology, Ludwig Maximilian University, Munich, Germany. Supervised by Prof. John Parsch.
			
			\item[11/2015--12/2015] 
			\textbf{MSc project:} Tree imbalance under the Protracted Birth Death model of speciation.\\ Department of Theoretical Research in Evolutionary Life Sciences, Groningen Institute for Evolutionary Life Sciences, University of Groningen, Groningen, the Netherlands. Supervised by Prof. Rampal S. Etienne.
			
			\item[06/2015--08/2015] 
			\textbf{MSc project:} Skeletal development and evolution of developmental genes in the Cuban gar (\textit{Atractosteus tristoechus}). In French.\\ 
			Institut des Sciences de l'Evolution de Montpellier, University of Montpellier, Montpellier, France. Supervised by Dr. Melanie Debiais-Thibaud.
			
		\end{cvlist}
		
		\section{Conferences}
		
		\begin{cvlist}{}
			
			\item[2022]
			\textbf{Conference talk:} Epistasis makes ecological speciation be driven by a speciation genome, not by speciation genes. Meeting of the Dutch Society for Evolutionary Biology (NLSEB), Groningen, the Netherlands.
			
			\item[2021] 
			\textbf{Conference talk:} The genomic signatures of speciation with gene networks. Modelling in Ecology and Evolution Meeting (MEEM), Lausanne, Switzerland.
			
			\item[2021] 
			\textbf{Conference talk:} Modeling speciation with gene networks. Meeting of the Dutch Society for Theoretical Biology (NVTB), Schoorl, the Netherlands.
			
			\item[2018] 
			\textbf{Poster:} Cladogenetic evolution of plumage coloration in birds of paradise. Evolution conference (ASN/SSB/SSE/ESEB), Montpellier, France.
			
			\item[2018] 
			\textbf{Poster:} Sexual selection plays a limited role in accelerating color evolution upon speciation in birds of paradise. Meeting of the Dutch Society for Evolutionary Biology (NLSEB), Ede, the Netherlands.
			
			\item[2017] 
			\textbf{Poster:} Adaptive divergence of dewlap coloration in \textit{Anolis sagrei}. Meeting of the European Society for Evoutionary Biology (ESEB), Groningen, the Netherlands.
			
		\end{cvlist}
		
		\section{Teaching}
		
		\subsection{University of Groningen (the Netherlands)}
		
		\begin{cvlist}{}

            \item[2024]
			\textbf{Lecturer \& Course coordinator:} Evolutionary Processes (BSc).

            \item[2023]
			\textbf{Lecturer:} Programming in C++ for biologists (BSc, MSc).
            
			\item[2023]
			\textbf{Lecturer \& Course coordinator:} Evolutionary Processes (BSc).

            \item[2023]
			\textbf{Content creator:} Evolutionary Theory (MSc).

            \item[2022] \textbf{Teaching assistant:} Evolutionary Processes (BSc). 

            \item[2021] \textbf{Teaching assistant:} Evolutionary Processes (BSc). 

            \item[2021] \textbf{Teaching assistant:} Behaviour, Ecology and Evolution (MSc). 
            
			\item[2020] \textbf{Teaching assistant:} Evolutionary Processes (BSc).
            
			\item[2020] \textbf{Teaching assistant:} Behaviour, Ecology and Evolution (MSc). 

            \item[2020] \textbf{Teaching assistant:} Programming in C++ for biologists (BSc, MSc).
			
			\item[2020] \textbf{Co-creator, Lecturer \& Coordinator:} Advanced data manipulation using R and the tidyverse --- tutorial for theoretical biologists (PhD).\\
            \url{https://github.com/pratikunterwegs/tres-tidy-tutorial}
            
			\item[2019] \textbf{Teaching assistant:} Programming in C++ for biologists (BSc, MSc).
			
		\end{cvlist}

        \section{Supervision}

        \subsection{University of Groningen (the Netherlands)}

        \begin{cvlist}{}

            \item[2020] \textbf{Supervision of MSc thesis:} Vasiliki (Celia) Tsapalou (MSc Ecology and Evolution).
			Inferring the Additive and Epistatic Genetic Architecture involved in Speciation Using Neural Networks.
			
			\item[2020] \textbf{Supervision of MSc essay:} Sebastian Mader (MSc Ecology and Evolution).
			Machine learning vs. “classical” statistics – A redundant but understandable differentiation.
			
			\item[2020] \textbf{Grading of MSc essay:} Israel Campo Bes (MSc in Ecology and Evolution).
			On the Origin of Genetic Dominance by Means of Natural Selection?
			
			\item[2020] \textbf{Supervision of BSc project:} Elsie Tata \& Robin Hamberg.
			Detecting speciation genetic architectures. Course: Modelling in the Life Sciences Research.
			
			\item[2019] \textbf{Supervision of MSc thesis:} Joris Damhuis (MSc Ecology and Evolution).
			Optimal choice and speciation.
			
			\item[2019] \textbf{Supervision of MSc mini-project:} Reinier de Vries.
			Generating a phylogenetic tree from a distance matrix using UPGMA and NJ. Course: Programming in C++ for biologists.
	
			\item[2019] \textbf{Supervision of BSc project:} Jelle Molenkamp \& Nicolette Tataru. The evolution of gene regulatory networks. Course: Modelling in the Life Sciences Research.
			
			\item[2018] \textbf{Supervision of BSc project:} Rik Nienhuis \& Bob Evenhuis. The effect of resource limitation and asymmetric competition on insular dwarfism and gigantism. Course: Community Ecology Research.

        \end{cvlist}
		
		%
		%\vspace{-1cm}
		\section{Peer Review}
		
		\begin{cvlist}{}
		\item[2022] Review for \textit{Nature Communications Biology}
		\item[2021] Review for \textit{Oikos}
		\item[2018] Review for \textit{Oikos}
		\item[2017] Review for \textit{Journal of Morphology}
		\end{cvlist}
		
		\section{Outreach}
		
		\begin{cvlist}{}

            \item[2025] \textbf{Voluntary lecturer \& Co-organizer} of the upcoming 2025 edition of the Crash Course in Evolutionary Biology, a free online course aimed at students from the Global South.\\
            \url{https://evobiocrashcourse.github.io/}

            \item[2024] \textbf{Voluntary lecturer \& Co-organizer} in the Crash Course in Evolutionary Biology.
            
			\item[2023] \textbf{Voluntary lecturer} in the Crash Course in Evolutionary Biology.
			
			\item[2021] \textbf{1-minute elevator pitch contest}, at NLSEB PhD/postdoc meeting, Ede, the Netherlands.
			
			\item[2019] \textbf{Podcast episode:} Meme Stream Episode 2: The tempo of evolution and the birds-of-paradise with Raphaël Scherrer.\\
			\url{https://open.spotify.com/episode/4lsaLONEsJtfeOObHPltq5}.
			
			\item[2018] \textbf{Outreach talk:} Cladogenetic evolution of plumage coloration in birds of paradise. Outreach seminar series in honor of writer Redmond O'Hanlon, Groningen Institute for Evolutionary Life Sciences, Groningen, the Netherlands.
	
		\end{cvlist}
		
		\section{Volunteering}
		
		\begin{cvlist}{}
		
			\item[03/2017] \textbf{Field assistant:} Capture of wild brown anoles (\textit{Anolis sagrei}) from the Bahamas for an experimental lizard colony at Harvard University. Department of Organismic and Evolutionary Biology, Harvard University, Cambridge, MA, USA. Supervised by Dr. Colin M. Donihue \& Prof. Jonathan B. Losos.
		
			\item[09/2016--02/2017] \textbf{Lab assistant:} Maintenance and animal husbandry for an experimental lizard colony at Harvard University. Department of Organismic and Evolutionary Biology, Harvard University, Cambridge, MA, USA. Supervised by Dr. Colin M. Donihue \& Dr. Anthony J. Geneva.
		
			\item[07/2014--08/2014] \textbf{Voluntary internship:} Maintenance and measurements in a mesocosm phytosanitary experiment in ecotoxicology. Research unit "Animals and Functionality of Animal Products", University of Lorraine, Nancy, France. Supervised by Dr. Marielle Thomas.
		
			\item[07/2013--08/2013] \textbf{Voluntary internship:} Behavioral observation and cognition experiments in a social network of captive rooks (\textit{Corvus frugilegus}). Department of Ecophysiology and Ethology, Centre National de la Recherche Scientifique (CNRS), Strasbourg, France. Supervised by Dr. Valérie Dufour.
		
			\item[2013] \textbf{Voluntary participation:} Inventory of the zoological collection of the Faculty of Sciences and Technology. University of Lorraine, Nancy, France. Supervised by Dr. Dominique Chardard.
		
		\end{cvlist}
		
		\section{Society Memberships}
		
		\begin{cvlist}{}
			
			\item[2021] \textbf{Member:} Society for the Study of Evolution (SSE). 
			
			\item[2021] \textbf{Member:} Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE).
			
			\item[2018--2019, 2021] \textbf{Member:} Dutch Society for Evolutionary Biology (NLSEB).
			
			\item[2017--2018] \textbf{Member:} European Society for Evolutionary Biology (ESEB).
			
			\item[2016--2019] \textbf{Member:} American Association for the Advancement of Science (AAAS).
			
		\end{cvlist}
		
		\section{Notable Skills}
		
		\begin{cvlist}{}
			
			\item Proficient in C++, R, Python, MATLAB , Mathematica, LaTeX, and working with high-performance computer clusters (HPC).
			\item Programming according to the test-driven development philosophy.
			\item Speaking native French, fluent English (C2), advanced Spanish (C1) and basic Dutch (A1).
			\item Managing life with type I diabetes since 2013.
			
		\end{cvlist}
	
		\section{Interests}
		
		\centering{improv comedy --- epistemiology and critical thinking --- salsa dancing --- martial arts --- natural history illustration --- cooking and baking --- fossils and minerals --- circus arts}
		
		% \vspace{1cm}
		
		\vfill
		\flushright{Compiled on \today}
		\date{}
		
	\end{cv}
	
\end{document}
\endinput
%%
%% End of file `cvtest.tex'.